Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs

### 2016-07-26 main_paper.tex
Convert algorithms to use wild bootstrap
This commit changes the first and second algorithm to use the
Wild bootstrap with general kernels. This commit also allows
the notation to be simplified a bit.

\begin{algorithm}[Bias estimation]\label{Alg1}
  Assume $h$ and $b$ are bandwidths as defined by Assumption~\ref{A2} and define
  \begin{align*}
    I_{-}(h) &= \{i : -h < X_{i} < 0\}, &
    I_{+}(h) &= \{i : 0 \leq X_{i} < h\}.
  \end{align*}
  Also define $M_{-}(h)$ and $M_{+}(h)$ to be the number of elements in $I_{-}(h)$ and
  $I_{+}(h)$ respectively, and $m_{-}(h,1),\dots,m_{-}(h,M_{-}(h))$ and
  $m_{+}(h,1),\dots,m_{+}(h,M_+(h))$ to be subsequences of $1,\dots,n$ that index
  $I_{-}(h)$ and $I_{+}(h)$, respectively.
  \begin{enumerate}
  \item Estimate local second order polynomials $\hat g_{-}$ and $\hat g_{+}$ using
    the observations in $I_{-}(b)$ and $I_{+}(b)$:
    \begin{align}
      \label{eq:2}
      \hat g_{-}(x)
      &= \hat\beta_{-,0} + \hat\beta_{-,1} x + \hat\beta_{-,2} x^{2},
      &\hat g_{+}(x)
      &= \hat\beta_{+,0} + \hat\beta_{+,1} x + \hat\beta_{+,2} x^{2}
    \end{align}
    with
    \begin{align*}
      \hat\beta_{-} &= \argmin_\beta \sum_{i \in I_-(b)}
      (Y_i - \beta_0 - \beta_1 X_i - \beta_2 X_i^2)^2 \\
      \hat\beta_{+} &= \argmin_\beta \sum_{i \in I_+(b)}
      (Y_i - \beta_0 - \beta_1 X_i - \beta_2 X_i^2)^2.
    \end{align*}
    Calculate the residuals
    \begin{equation}
      \label{eq:3}
      \hat\varepsilon_{i} =
      \begin{cases}
        Y_{i} - \hat g_-(X_{i}) & \textif\ X_{i} < 0 \\
        Y_{i} - \hat g_+(X_{i}) & \otherwise.
      \end{cases}
    \end{equation}
  \item Repeat the following steps $B_{1}$ times to produce the
    bootstrap estimates $\hat{\tau}_{1}^{*}(h),\dots,\hat\tau_{B_{1}}^{*}(h)$. For the
    $k$th value:
    \begin{enumerate}
    \item Draw an i.i.d. sample of size $M_-(b)$ from
      $\{\hat\varepsilon_i : i \in I_-(b)\}$ and one of size $M_+(b)$ from
      $\{\hat\varepsilon_i : i \in I_+(b)\}$. Let $\varepsilon_{-,i}^{*}$ and
      $\varepsilon_{+,i}^{*}$ denote the $i$th element of each sample and
      construct
      \begin{align*}
        Y_{-,m_-(b,i)}^* &= \hat g_-(X_{m_-(b,i)}) + \varepsilon_{-,i}^{*} &
        Y_{+,m_+(b,i)}^* &= \hat g_+(X_{m_-(b,i)}) + \varepsilon_{+,i}^{*}.
      \end{align*}
    \item Calculate $\hat\mu_+^*(h)$ and $\hat\mu_-^*(h)$ by estimating the
      local linear model on the bootstrap data set:\footnote{%
        Note that the indices of summation are chosen to correspond to the
        indices of the variables generated in the previous step.} %
      \begin{align*}
        \hat\mu_-^*(h)
        &= \argmin_{\mu} \min_{\beta} \ssum[-]{i}{h}
          (Y_i^* - \mu - \beta X_i^*)^2 \\
        \hat\mu_+^*(h)
        &= \argmin_{\mu} \min_{\beta} \ssum[+]{i}{h}
          (Y_i^* - \mu - \beta X_i^*)^2.
      \end{align*}
    \item Save $\hat\tau^*_k(h) = \hat\mu_+^*(h) - \hat\mu_-^*(h)$.
    \end{enumerate}
  \item Estimate the bias as
    \begin{equation}
      \label{eq:9}
      \Delta^*(h,b) = \tfrac{1}{B_1} \sum_{k=1}^{B_1} \hat\tau^*_k(h) -
      \big[\hat g_+(0) - \hat g_-(0)\big].
    \end{equation}
  \end{enumerate}
\end{algorithm}
Note that $\hat g_+(0) - \hat g_-(0)$ is the true treatment effect under the
distribution induced by this bootstrap. The bootstrap estimator works by
constructing an approximate DGP with known properties. As the dataset gets
larger, the approximate DGP mimics the unknown real DGP more closely, and the
population parameter values in the bootstrap DGP can become accurate estimates
of the true parameter values in the real DGP.

@@

\begin{algorithm}[Confidence intervals]\label{Alg2}
  Define the same notation as in Algorithm~\ref{Alg1}.
  \begin{enumerate}
  \item Estimate $\hat{g}_{+}$ and $\hat{g}_{-}$ and generate the residuals
    $\hat\varepsilon_i$ just as in Algorithm~\ref{Alg1}.
  \item Repeat the following steps $B_{2}$ times to produce the
    bootstrap estimates
    $\hat\tau_1^{\prime*}(h,b), \dots, \hat\tau_{B_{2}}^{\prime*}(h,b)$. For the
    $k$th value:
    \begin{enumerate}
    \item Draw an i.i.d. sample of size $M_-(b)$ from
      $\{\hat\varepsilon_i : i \in I_-(b)\}$ and one of size $M_+(b)$ from
      $\{\hat\varepsilon_i : i \in I_+(b)\}$. Let $\varepsilon_{-,i}^{*}$ and
      $\varepsilon_{+,i}^{*}$ denote the $i$th element of each sample and
      construct
      \begin{align*}
        Y_{-,m_-(b,i)}^* &= \hat g_-(X_{m_-(b,i)}) + \varepsilon_{-,i}^{*} &
        Y_{+,m_+(b,i)}^* &= \hat g_+(X_{m_{+}(b,i)}) + \varepsilon_{+,i}^{*}.
      \end{align*}
    \item Calculate $\hat\mu_+^*(h)$ and $\hat\mu_-^*(h)$ by estimating the
      local linear model on the bootstrap data set:
      \begin{align*}
        \hat\mu_-^*(h)
        &= \argmin_{\mu} \min_{\beta} \ssum[-]{i}{h}
          (Y_i^* - \mu - \beta X_i^*)^2 \\
        \hat\mu_+^*(h)
        &= \argmin_{\mu} \min_{\beta} \ssum[+]{i}{h}
          (Y_i^* - \mu - \beta X_i^*)^2.
      \end{align*}
    \item Apply Algorithm~\ref{Alg1} to the bootstrapped data set,
      \begin{multline*}
        (Y_{-,m_-(b,1)}^{*}, X_{-,m_-(b,1)}),\dots,
        (Y_{-,m_-(b,M_-(b))}^{*},X_{-,m_-(b,M_-(b))}), \\
        (Y_{+,m_+(b,1)}^{*}, X_{+,m_+(b,1)}),\dots,
        (Y_{+,m_+(b,M_+(b))}^{*},X_{+,m_+(b,M_+(b))})
      \end{multline*}
      using the same bandwidths $h$ and $b$ that are used in the rest of this
      algorithm but reestimating all of the local polynomials on the bootstrap
      data. Generate $B_1$ new bootstrap samples and let $\Delta^{**}(h,b)$
      represent the bias estimator returned by Algorithm~\ref{Alg1}.
    \item Save the bias-corrected estimator
      $\hat\tau_k^{\prime*}(h,b) = \hat\mu_+^*(h) - \hat\mu_i^*(h)
      - \Delta^{**}(h,b)$.
    \end{enumerate}
  \item Use the empirical CDF of
    $\hat\tau_1^{\prime*}(h,b),\dots \hat\tau_{B_2}^{\prime*}(h,b)$ to
    construct confidence intervals, etc.
  \end{enumerate}
\end{algorithm}

>>>>

\begin{algorithm}[Bias estimation]\label{Alg1}
  Assume $h$ and $b$ are bandwidths as defined by Assumption~\ref{A2} and define
  \begin{align*}
    I_{-} &= \{i : X_i < 0 \}, &
    I_{+} &= \{i : X_i > 0 \}.
  \end{align*}
  Also define $M_{-}$ and $M_{+}$ to be the number of elements in $I_{-}$ and
  $I_{+}$ respectively, and $m_{-}(1),\dots,m_{-}(M_{-})$ and
  $m_{+}(1),\dots,m_{+}(M_+)$ to be subsequences of $1,\dots,n$ that index
  $I_-$ and $I_+$, respectively.
  \begin{enumerate}
  \item Estimate local second order polynomials $\hat g_{-}$ and $\hat g_{+}$ using
    the observations in $I_-$ and $I_+$ and the kernel $K_{b}(X_{i})$:
    \begin{align}
      \label{eq:2}
      \hat g_{-}(x)
      &= \hat\beta_{-,0} + \hat\beta_{-,1} x + \hat\beta_{-,2} x^{2},
      &\hat g_{+}(x)
      &= \hat\beta_{+,0} + \hat\beta_{+,1} x + \hat\beta_{+,2} x^{2}
    \end{align}
    with
    \begin{align*}
      \hat\beta_{-} &= \argmin_\beta \sum_{i \in I_-}
      (Y_i - \beta_0 - \beta_1 X_i - \beta_2 X_i^2)^{2} K_{b}(X_{i}) \\
      \hat\beta_{+} &= \argmin_\beta \sum_{i \in I_+}
      (Y_i - \beta_0 - \beta_1 X_i - \beta_2 X_i^2)^{2} K_{b}(X_{i}).
    \end{align*}
    Let
    \[
      \hat g(x) = \begin{cases}
        \hat g_-(x) & \textif\ x < 0 \\
        \hat g_+(x) & \otherwise
      \end{cases}
    \]
    and calculate the residuals $\hat\varepsilon_{i} = Y_i - \hat g(X_i)$.
  \item Repeat the following steps $B_{1}$ times to produce the
    bootstrap estimates $\hat{\tau}_{1}^{*}(h),\dots,\hat\tau_{B_{1}}^{*}(h)$. For the
    $k$th value:
    \begin{enumerate}
    \item Draw i.i.d.\ random variables $e_i^{*}$ with mean zero, variance one,
      and bounded fourth moments independent of the original data and
      construct
      \begin{align*}
        \varepsilon_i^{*} &= \hat{\varepsilon}_i e^{*}_i,
        \intertext{and}
        Y_i^{*} &= \hat g(X_i) + \varepsilon_i^{*}.
      \end{align*}
    \item Calculate $\hat\mu_+^*(h)$ and $\hat\mu_-^*(h)$ by estimating the
      local linear model on the bootstrap data set
      \begin{align*}
        \hat\mu_-^*(h)
        &= \argmin_{\mu} \min_{\beta} \sum_{i \in I_{-}}
          (Y_i^* - \mu - \beta X_i)^2 K_{h}(X_{i}) \\
        \hat\mu_+^*(h)
        &= \argmin_{\mu} \min_{\beta} \sum_{i \in I_{+}}
          (Y_i^* - \mu - \beta X_i)^2 K_{h}(X_{i}).
      \end{align*}
    \item Save $\hat\tau^*_k(h) = \hat\mu_+^*(h) - \hat\mu_-^*(h)$.
    \end{enumerate}
  \item Estimate the bias as
    \begin{equation}
      \label{eq:9}
      \Delta^*(h,b) = \tfrac{1}{B_1} \sum_{k=1}^{B_1} \hat\tau^*_k(h) -
      \big[\hat g_+(0) - \hat g_-(0)\big].
    \end{equation}
  \end{enumerate}
\end{algorithm}
Note that $\hat g_+(0) - \hat g_-(0)$ is the true treatment effect under the
distribution induced by this bootstrap. The bootstrap estimator works by
constructing an approximate DGP with known properties. As the dataset gets
larger, the approximate DGP mimics the unknown real DGP more closely, and the
population parameter values in the bootstrap DGP can become accurate estimates
of the true parameter values in the real DGP.

@@

\begin{algorithm}[Confidence intervals]\label{Alg2}
  Define the same notation as in Algorithm~\ref{Alg1}.
  \begin{enumerate}
  \item Estimate $\hat{g}_{+}$ and $\hat{g}_{-}$ and generate $\hat g(\cdot)$
    and the residuals $\hat\varepsilon_i$ just as in Algorithm~\ref{Alg1}.
  \item Repeat the following steps $B_{2}$ times to produce the
    bootstrap estimates
    $\hat\tau_1^{\prime*}(h,b), \dots, \hat\tau_{B_{2}}^{\prime*}(h,b)$. For the
    $k$th value:
    \begin{enumerate}
    \item Draw i.i.d.\ random variables $e_i^{*}$ with mean zero, variance one,
      and bounded fourth moments independent of the original data and
      construct
      \begin{align*}
        \varepsilon_i^{*} &= \hat{\varepsilon}_i e^{*}_i,
        \intertext{and}
        Y_i^{*} &= \hat g(X_i) + \varepsilon_i^{*}.
      \end{align*}
    \item Calculate $\hat\mu_+^*(h)$ and $\hat\mu_-^*(h)$ by estimating the
      local linear model on the bootstrap data set:
      \begin{align*}
        \hat\mu_-^*(h)
        &= \argmin_{\mu} \min_{\beta} \sum_{i \in I_{-}}
          (Y_{i}^{*} - \mu - \beta X_{i})^{2}K_{h}(X_{i}) \\
        \hat\mu_+^*(h)
        &= \argmin_{\mu} \min_{\beta} \sum_{i \in I_{+}}
          (Y_{i}^{*} - \mu - \beta X_{i})^{2}K_{h}(X_{i}).
      \end{align*}
    \item Apply Algorithm~\ref{Alg1} to the bootstrapped data set
      using the same bandwidths $h$ and $b$ that are used in the rest of this
      algorithm but reestimating all of the local polynomials on the bootstrap
      data. Generate $B_1$ new bootstrap samples and let $\Delta^{**}(h,b)$
      represent the bias estimator returned by Algorithm~\ref{Alg1}.
    \item Save the bias-corrected estimator
      $\hat\tau_k^{\prime*}(h,b) = \hat\mu_+^*(h) - \hat\mu_i^*(h)
      - \Delta^{**}(h,b)$.
    \end{enumerate}
  \item Use the empirical CDF of
    $\hat\tau_1^{\prime*}(h,b),\dots \hat\tau_{B_2}^{\prime*}(h,b)$ to
    construct confidence intervals, etc.
  \end{enumerate}
\end{algorithm}
